\documentclass[11pt]{article}
\input{vars.tex}
\input{preamble.tex}
\renewcommand{\DocFooterTitle}{Data Processing Addendum to \MSARef}

\begin{document}

\DocTitle{DATA PROCESSING ADDENDUM (DPA) \\[0.3em] \large to Master Services Agreement \MSARef}

\begin{center}
Effective Date: \EffectiveDate
\end{center}

This Data Processing Addendum (the ``DPA'') is entered into by and between:

\textbf{\ClientName}\ (the ``Controller''),

and

\textbf{\VendorName}\ (the ``Processor'').

This DPA forms an integral part of the Master Services Agreement referenced above (the
``MSA'') and is subject to all terms and conditions thereof. In the event of any conflict
between this DPA and the MSA, the terms of this DPA shall prevail with respect to the
processing of Personal Data.

WHEREAS, the Controller and Processor have entered into the MSA pursuant to which the
Processor will provide certain services to the Controller involving the processing of
Personal Data;

WHEREAS, the Parties wish to ensure compliance with Regulation (EU) 2016/679 (the ``GDPR'')
and other applicable data protection laws, particularly Article 28 thereof;

NOW, THEREFORE, the Parties agree as follows:

\section*{1. Definitions}
\textbf{1.1 ``Personal Data''} means any information relating to an identified or
identifiable natural person.

\textbf{1.2 ``Processing''} means any operation or set of operations performed on Personal
Data.

\textbf{1.3 ``Data Subject''} means the identified or identifiable natural person to whom
Personal Data relates.

\textbf{1.4 ``Subprocessor''} means any third party engaged by the Processor that processes
Personal Data on behalf of the Controller.

\section*{2. Processing Specifications}
The Processor shall process Personal Data solely on behalf of and in accordance with the
documented instructions of the Controller, as set forth in this DPA and the MSA.

\textbf{2.1 Categories of Data Subjects:} \DataSubjectCategories\ of the Controller.

\textbf{2.2 Nature and Purpose of Processing:} Real-time transaction authorization,
settlement capture, transaction routing, card processing routines, and related payment
facilitation activities necessary for the performance of the Services under the MSA.

\textbf{2.3 Types of Personal Data:} Full names, billing addresses, credit card numbers
(Primary Account Numbers or PANs), card expiration dates, card verification values (where
applicable), account histories, transaction records, and any other personal data provided
by the Controller or generated during the provision of Services.

\textbf{2.4 Duration of Processing:} For the duration of the MSA and for a period not
exceeding \PostTerminationRetentionDays\ days after termination or expiry thereof, unless
otherwise instructed by the Controller.

\section*{3. Subprocessors}
\textbf{3.1} The Processor shall not engage any Subprocessor without the prior written
consent of the Controller.

\textbf{3.2} The Controller hereby authorizes the Processor to engage the following
Subprocessors as of the Effective Date:
\begin{itemize}[leftmargin=2em]
  \item \SubprocessorOneName, Region: \SubprocessorOneRegion, for \SubprocessorOnePurpose.
  \item \SubprocessorTwoName, for \SubprocessorTwoPurpose.
\end{itemize}

\textbf{3.3} The Processor shall enter into written agreements with each Subprocessor that
impose obligations no less protective than those set out in this DPA.

\textbf{3.4} The Processor shall notify the Controller in writing at least
\SubprocessorNoticeDays\ days in advance of any intended addition or replacement of a
Subprocessor. The Controller may object to such change within \SubprocessorObjectionDays\
days. If the Controller objects, the Parties shall work together in good faith to resolve
the objection or find an alternative solution.

\section*{4. Technical and Organizational Measures (TOMs)}
The Processor shall implement and maintain appropriate technical and organizational measures
to ensure the security of Personal Data, including but not limited to:
\begin{enumerate}[leftmargin=2em]
  \item Encryption of Personal Data at rest using \PCIEncryptionStandard\ or equivalent
  industry-standard algorithm.
  \item Encryption of Personal Data in transit using \PCITransitStandard\ or higher.
  \item Strict access controls, including role-based access, multi-factor authentication,
  and least privilege principles.
  \item Regular security audits, vulnerability scanning, and penetration testing.
  \item Employee training on data protection and confidentiality obligations.
  \item Incident response procedures and business continuity measures.
  \item Measures to ensure the ongoing confidentiality, integrity, availability, and
  resilience of processing systems.
\end{enumerate}

The Processor shall provide the Controller with a summary of its current TOMs upon request
and shall notify the Controller of any material changes.

\section*{5. Data Breach Notification}
\textbf{5.1} In the event of a confirmed or reasonably suspected Personal Data Breach
affecting Controller Personal Data, the Processor shall notify the Controller via
\BreachNotificationEmail\ within exactly \BreachNotificationHours\ hours of initial
discovery.

\textbf{5.2} Such notification shall include, at a minimum: (i) a description of the nature
of the breach, (ii) the categories and approximate number of Data Subjects and records
concerned, (iii) the likely consequences, and (iv) the measures taken or proposed to address
the breach.

\textbf{5.3} The Processor shall cooperate fully with the Controller in investigating and
remediating any such breach and in fulfilling the Controller's obligations under Articles 33
and 34 of the GDPR.

\section*{6. Assistance to the Controller}
The Processor shall assist the Controller in ensuring compliance with GDPR obligations,
including with respect to data subject rights, data protection impact assessments, and
prior consultations with supervisory authorities. Such assistance shall be provided at the
Controller's reasonable request and expense (unless the request arises from the Processor's
breach).

\section*{7. Return or Deletion of Personal Data}
Upon termination or expiry of the MSA, or at any time upon the Controller's request, the
Processor shall, at the Controller's choice, return or securely delete all Personal Data and
certify in writing that it has done so, except to the extent retention is required by
applicable law.

\section*{8. Audits}
The Controller or its designated auditor shall have the right to audit the Processor's
compliance with this DPA upon \AuditNoticeContext, not more than \AuditFrequency, unless
there is reasonable suspicion of non-compliance.

\section*{9. Governing Law}
This DPA shall be governed by \DPAGoverningLaw.

IN WITNESS WHEREOF, the Parties have executed this DPA as of the Effective Date.

\SignBlock{\ClientName\ (Controller)}{\VendorName\ (Processor)}

\newpage
\section*{Appendix A: Processing Details}

\begin{longtable}{p{4cm} p{9cm}}
\toprule
\textbf{Element} & \textbf{Description} \\
\midrule
\endhead
Categories of Data Subjects & \DataSubjectCategories \\
Nature of Processing & Real-time authorization, settlement capture, and transaction routing \\
Types of Personal Data & Full names, billing addresses, credit card numbers (PANs), card
expiration dates, account histories, transaction records \\
Duration & Term of the MSA plus up to \PostTerminationRetentionDays\ days post-termination \\
\bottomrule
\end{longtable}

\section*{Appendix B: Approved Subprocessors}

\begin{longtable}{p{4cm} p{4cm} p{5cm}}
\toprule
\textbf{Subprocessor} & \textbf{Location / Region} & \textbf{Purpose} \\
\midrule
\endhead
\SubprocessorOneName & \SubprocessorOneRegion & \SubprocessorOnePurpose \\
\SubprocessorTwoName & \SubprocessorTwoRegion & \SubprocessorTwoPurpose \\
\bottomrule
\end{longtable}

\end{document}
