\documentclass[11pt]{article}
\input{vars.tex}
\input{preamble.tex}
\renewcommand{\DocFooterTitle}{Master Services Agreement \MSARef}

\begin{document}

\DocTitle{MASTER SERVICES AGREEMENT \\[0.3em] \large Document Reference: \MSARef}

\begin{center}
Effective Date: \EffectiveDate
\end{center}

This Master Services Agreement (the ``Agreement'') is entered into as of the Effective Date
set forth above, by and between:

\textbf{\ClientName}, a \ClientLegalForm\ organized and existing under the laws of
\ClientCountry, having its registered office at \ClientAddress\ (hereinafter referred to as
the ``Client''),

and

\textbf{\VendorName}, a limited liability company organized and existing under the laws of
the State of \VendorState, United States of America, having its principal place of business
at \VendorAddress\ (hereinafter referred to as the ``Provider'').

(Each a ``Party'' and collectively, the ``Parties'').

WHEREAS, Client desires to engage Provider to perform certain services related to
high-volume payment processing;

WHEREAS, Provider possesses the expertise, infrastructure, and capabilities necessary to
provide such services;

WHEREAS, the Parties wish to set forth the terms and conditions under which Provider will
provide the Services to Client;

NOW, THEREFORE, in consideration of the mutual promises and covenants contained herein, and
for other good and valuable consideration, the receipt and sufficiency of which are hereby
acknowledged, the Parties agree as follows:

\section*{1. Definitions}
\textbf{1.1 Customer Data} shall mean all data, information, or materials provided by Client
to Provider or generated by Provider in the course of performing the Services, including but
not limited to cardholder data, transaction records, account information, personally
identifiable information, and any derivatives or aggregations thereof. Customer Data shall
be deemed Confidential Information of Client.

\textbf{1.2 Proprietary Information} shall mean any and all non-public information disclosed
by one Party (the ``Disclosing Party'') to the other Party (the ``Receiving Party''),
whether orally, in writing, or by any other means, that is designated as confidential or
that, given the nature of the information or the circumstances surrounding its disclosure,
reasonably should be understood to be confidential.

\textbf{1.3 Core Production Infrastructure} shall mean Client's live operational
environment, including but not limited to primary transactional databases, payment
switches, card management systems, secure network segments, and all associated hardware,
software, and network components that process, store, or transmit production financial
transactions and Customer Data in real-time.

\section*{2. Scope of Work}
\textbf{2.1} Provider shall perform the Services as described in one or more Statements of
Work executed by the Parties, which shall be incorporated herein by reference. The Services
shall include, without limitation, high-volume card processing routines, authorization,
clearing, settlement, and related payment facilitation activities.

\textbf{2.2} Provider shall directly interface with Client's live transactional databases
and Core Production Infrastructure in accordance with the security protocols, technical
specifications, and integration requirements set forth in the applicable Statement of Work
and any security addendum attached hereto. All such interfaces shall be conducted through
secure, encrypted channels using industry-standard protocols.

\textbf{2.3} Provider shall maintain all necessary licenses, certifications, and compliance
with applicable laws, regulations, and card scheme rules (including but not limited to PCI
DSS) at all times during the Term. Provider shall be responsible for the performance of its
subcontractors, if any, to the same extent as for its own performance.

\section*{3. Fees \& Financial Terms}
\textbf{3.1 Fees.} In consideration for the Services provided by Provider, Client shall pay
Provider the fees set forth in the applicable Statement of Work (the ``Fees'').

\textbf{3.2 Billing Cycles.} Provider shall invoice Client on a monthly basis, in arrears,
for Services rendered during the preceding calendar month.

\textbf{3.3 Payment Schedules.} Client shall remit payment of each undisputed invoice within
\PaymentTermDays\ days of receipt. Payments shall be made in United States Dollars via wire
transfer to the account designated by Provider. Late payments shall accrue interest at the
rate of \LatePaymentRate\ per month or the maximum rate permitted by law, whichever is less.

\textbf{3.4 Taxes.} Fees are exclusive of all applicable taxes, duties, and governmental
charges. Client shall be responsible for payment of all such taxes, excluding taxes based on
Provider's net income.

\section*{4. Indemnification}
\textbf{4.1 Mutual Indemnification.} Each Party shall indemnify, defend, and hold harmless
the other Party and its affiliates, officers, directors, employees, and agents from and
against any and all claims, damages, losses, liabilities, costs, and expenses (including
reasonable attorneys' fees) arising out of or relating to (i) any breach of this Agreement
by the indemnifying Party, or (ii) the gross negligence or willful misconduct of the
indemnifying Party.

\textbf{4.2 Liability Cap.} Subject to the exceptions set forth in Section 4.3, the total
aggregate liability of Provider to Client under this Agreement, whether in contract, tort
(including negligence), or otherwise, shall not exceed \LiabilityCapAmount.

\textbf{4.3 Uncapped Liabilities.} Notwithstanding the foregoing, the liability cap set
forth in Section 4.2 shall not apply to: (i) Provider's obligations under indemnification
for gross negligence or willful misconduct; (ii) any breach of confidentiality obligations
with respect to Customer Data or Proprietary Information; (iii) willful data security
failures, including but not limited to breaches of PCI DSS, unauthorized access to Core
Production Infrastructure, or compromise of Customer Data; or (iv) any liability that
cannot be limited by applicable law. In such cases, liability shall be uncapped.

\section*{5. Term \& Termination}
\textbf{5.1 Term.} This Agreement shall commence on the Effective Date and shall continue
in full force and effect for a period of \InitialTermMonths\ months thereafter (the
``Initial Term''), unless earlier terminated in accordance with this Section.

\textbf{5.2 Termination for Cause.} Either Party may terminate this Agreement immediately
upon written notice to the other Party if: (i) the other Party materially breaches any
provision of this Agreement and fails to cure such breach within \CureDays\ days after
receipt of notice thereof; or (ii) the other Party becomes insolvent, files for bankruptcy,
or ceases to conduct business in the ordinary course.

\textbf{5.3 Security Certification Termination Right.} Client shall have the right to
terminate this Agreement immediately for cause, without cure period, if Provider fails to
maintain valid and current industry security certifications, including but not limited to
\RequiredCertifications, or any other certification required by applicable card schemes or
regulatory authorities. Upon such termination, Provider shall promptly return or destroy all
Customer Data and provide a certification of compliance signed by an officer of Provider.

\textbf{5.4 Effects of Termination.} Upon termination or expiration: (i) all rights and
licenses granted hereunder shall immediately cease; (ii) Provider shall cease all use of and
return or destroy Customer Data and Proprietary Information; (iii) Client shall pay all
outstanding undisputed Fees for Services rendered prior to the effective date of
termination; and (iv) the provisions of Sections 1, 4, 6, 7, and any surviving obligations
shall survive termination.

\section*{6. Governing Law and Dispute Resolution}
This Agreement shall be governed by the laws of the State of \GoverningLawState, without
regard to conflict of laws principles. Any disputes arising under this Agreement shall be
resolved exclusively in the state or federal courts located in \VenueCounty, and the Parties
hereby consent to the personal jurisdiction and venue thereof.

\section*{7. Confidentiality}
Each Party agrees to maintain the confidentiality of the other Party's Proprietary
Information and Customer Data using at least the same degree of care as it uses for its own
similar information, but in no event less than reasonable care. This obligation shall
survive for \ConfidentialitySurvivalYears\ years following termination of this Agreement.

\section*{8. Miscellaneous}
\textbf{8.1} This Agreement, together with any Statements of Work, constitutes the entire
agreement between the Parties and supersedes all prior understandings.

\textbf{8.2} No amendment shall be effective unless in writing and signed by both Parties.

\textbf{8.3} If any provision is held invalid, the remainder shall continue in full force.

\textbf{8.4} Neither Party may assign this Agreement without the prior written consent of
the other Party, except in connection with a merger or acquisition of substantially all
assets.

IN WITNESS WHEREOF, the Parties have executed this Agreement as of the Effective Date.

\SignBlock{\ClientName\ (Client)}{\VendorName\ (Provider)}

\end{document}
